### 2014-10-29 Draft/abstract.tex
ignored generated files
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

\textbf{Objective}: We propose \tool, an automated approach to infer
temporal constraints from API documents.

\textbf{Background}: Temporal constraints of an Application Programming
Interface (API) are the allowed sequences of invocations of
methods from the API. These constraints govern the secure and robust
operation of client software using the API.

@@

\textbf{Results}: To evaluate our approach, we apply \tool\ to infer temporal
constraints from commonly used package \CodeIn{java.io} in the
JDK API and from the \amazonAPI. Our results show
that \tool\ effectively identifies constraint sentences (from over
3900 API sentences) with the average precision, recall, and F-score
of 65.0\%, 72.2\%, and 68.4\%, respectively. Furthermore, \tool\
also achieves an accuracy of 70\% in inferring 63 temporal constraints
from these sentences.

>>>>

%\textbf{Objective}: We propose \tool, an automated approach to infer
%temporal constraints from API documents.

\textbf{Objective}: The goal of this work is to assist developers construct
web Application Programming Interface (API) clients that comply with 
temporal constraints of the API thorough the inference and formalization of these constraints found in natural language text in API documents.

\textbf{Background}: Temporal constraints of an API
are the allowed sequences of invocations of
methods from the API. These constraints govern the secure and robust
operation of client software using the API.

@@

\textbf{Results}: To evaluate our approach, we apply \tool\ to infer temporal
constraints from \amazonAPI, \paypalAPI and commonly used package \CodeIn{java.io} in the
JDK API.
Our results show that \tool\ effectively identifies constraint sentences (from over
3900 API sentences) with the average precision, recall, and F-score
of 65.0\%, 72.2\%, and 68.4\%, respectively. Furthermore, \tool\
also achieves an accuracy of 70\% in inferring 63 temporal constraints
from these sentences.

### 2014-10-29 Draft/formal.tex
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

In this section we describe various classes of temporal constraints using formal temporal logic.
In computer science, temporal Logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al~\cite{lo2009mining}

\textbf{Method Invocation}: 
We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as Method Invocation,
who define event as \textit{``any concrete or abstract representation of a program state''}. 
In particular, we propose the notion of method invocation analogous to the events as methods invocation,
where each method invocation is represented as a tuple which is an ordered set of strings. 
A method invocation is captured as the Tuple <$T$><\CodeIn{str1, str2, str3}...>, where \CodeIn{str1, str2, str3}... are string values,
that belong to set of all strings.
In particular, the method invocation tuple <$T$> captures information about the return value, enclosing type, name, and the parameter types of the method.
Thus Tuple[String, Bar, foo, Integer, Integer] represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}

\textbf{Method Invocation Predicates}: We define method predicate as a predicate E over method invocations.
We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method Predicate $\xi$.
In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
In particular, the predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}. The simplest form of these predicates is of type \CodeIn{\$2 = sym} which refer to method invocations of name \CodeIn{sym}.

@@

\item \textit{Forward Eventual Operator $\xi_1 \xrightarrow{*} \xi_2$}
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$

\item \textit{Backward Eventual Operator $\xi_1 \xleftarrow{*} \xi_2$}
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$

\item \textit{Forward Alternation Operator $\xi_1 \xrightarrow{a} \xi_2$}
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between

\item \textit{Backward Alternation Operator $\xi_1 \xleftarrow{a} \xi_2$}
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
\end{enumerate}

In addition to these operators we propose two additional operators:
\begin{enumerate}
\item Forward Prohibition Operator $\xi_1 \nrightarrow \xi_2$
occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$

\item Backward Prohibition Operator $\xi_1 \nleftarrow \xi_2$
occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
\end{enumerate}

@@

In summary, we extended the formalism for temporal rules previously proposed by Lo et al~\cite{lo2009mining} to express temporal constraints.
We obtain different classes of temporal constraints by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.

>>>>

In this section we describe various classes of temporal constraints using formal temporal logic.
In computer science, temporal Logic is a system of rules and symbols that are used to express and reason about prepositions pertaining to time.
We next present an extension to the temporal logic for API method invocation related rules proposed by Lo et al.~\cite{lo2009mining}

\textbf{Method Invocation}: 
We adapt the definition of events proposed by Lo et al.~\cite{lo2009mining} as method invocation.
They define event as \textit{``any concrete or abstract representation of a program state''}. 
We propose the notion of method invocation analogous to the events,
where each method invocation is represented as a tuple which is an ordered set of strings. 
A method invocation is captured as the Tuple <$T$><\CodeIn{str1, str2, str3}...>, where \CodeIn{str1, str2, str3}... are string values,
that belong to set of all strings.
The method invocation tuple <$T$> captures information about the return value, enclosing type, name, and the parameter types of the method.
Therefore a tuple <$T$><\CodeIn{String, Bar, foo, Integer, Integer}> represents a method \CodeIn{foo} enclosed by the type \CodeIn{Bar},
that accepts two parameters of type \CodeIn{Integer} and a return value of type \CodeIn{String}. 
For better readability mnemonic representation of the preceding tuple is \CodeIn{String<-Bar.foo(Integer, Integer);}

\textbf{Method Invocation Predicates}: We define method predicate as a predicate $E$ over method invocations.
We reuse the notations proposed by Lo et al.~\cite{lo2009mining} $m \vdash \xi$ to denote that method invocation $m$ satisfies method predicate $\xi$.
In context of \tool, method predicates combines a method name and the enclosing type with potential constraints on the return types and parameter types. 
The predicates are modeled after \textit{equality constraints predicates}, and are represented as \CodeIn{\$i=sym}, where \CodeIn{i} is a non-negative integer and \CodeIn{sym} is the primitive string value and defined as: a method invocation $m$ satisfies a predicates \CodeIn{\$i=sym} iff \CodeIn{m[i]=sym}. The simplest form of these predicates is of type \CodeIn{\$2 = sym} which refer to method invocations of name \CodeIn{sym}.

@@

\item \textit{Forward Eventual Operator ($\xi_1 \xrightarrow{*} \xi_2$)}:
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$

\item \textit{Backward Eventual Operator: ($\xi_1 \xleftarrow{*} \xi_2$)}:
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$

\item \textit{Forward Alternation Operator ($\xi_1 \xrightarrow{a} \xi_2$)}:
occurrence of $\xi_1$ must be eventually followed by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between

\item \textit{Backward Alternation Operator ($\xi_1 \xleftarrow{a} \xi_2$)}:
occurrence of $\xi_1$ must be preceded by occurrence of $\xi_2$ and $\xi_1$ cannot occur in between
\end{enumerate}

We extend these operators by proposing two additional operators:
\begin{enumerate}
\item Forward Prohibition Operator ($\xi_1 \nrightarrow \xi_2$):
occurrence of $\xi_1$ cannot be followed by occurrence of $\xi_2$

\item Backward Prohibition Operator ($\xi_1 \nleftarrow \xi_2$):
occurrence of $\xi_1$ cannot be preceded by the occurrence of $\xi_2$
\end{enumerate}

@@

In summary, we extended the formalism for temporal rules previously proposed by Lo et al.~\cite{lo2009mining} to express temporal constraints.
We obtain different classes of temporal constraints by varying: 1) the temporal operators allowed, b) the method-invocation predicates allowed, and 3) the degree of quantification allowed.

### 2014-10-29 Draft/introduction.tex
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

The increasing reach of internet has fueled the growth of web
Application Programming Interfaces (API). The ProgrammableWeb
reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
These APIs are being combined in interesting ways by
application developers creating third-party applications using
these APIs to provide
value added service. For instance, Netflix API leverages Facebook
web API to assist users with finding movies that their friends are
interested in.

Web APIs, like traditional APIs have rules or constraints governing
the use of the API that must be followed. One such type of
constraints are temporal constraints [2], which are the allowed sequences
of invocations of methods from the API. Non-compliance
to such constraints can result in faulty applications that are unreliable
to use and may even result in financial losses. Thus, formal
analysis tools such as model checker and runtime verifiers are of
high value in detecting the violations of the temporal constraints as
defects~\cite{lee2012towards}.

Typically, temporal constraints are described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
in \amazonAPI\ documentation describe temporal constraints.
However, existing verification tools, which typically accept only formal constraints,
cannot use the natural language constraints from API documents.

@@

Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified in order to infer temporal constraints on the method but such method referencing is often implicit.
Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method-invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively time and resource intensive.
To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

@@

\begin{itemize}
	\item An NLP-based approach that effectively infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on commonly used package \CodeIn{java.io} from the JDK API and from \amazonAPI. 
\end{itemize}

@@

%First, relying just on type information will result in an incomplete list of temporal constraints. 
In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
Voilations are easily detected by the IDE's
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
However, using type system to detect temporal constraints in context of web APIs will result
in a lot of false positives as web APIs work only on basic types such as
\CodeIn{strings} and \CodeIn{numbers}.
Use of basic datatype by web-apis result in search space explosion.
Furthermore, we observed that temporal constraints re not limited to the type definitions

Our proposed approach extends the existing approaches to address the challenge.

However, temporal constraints are not limited by the type definitions
(i.e, requirements on the type of input parameters),
and are currently expressed mostly in natural language in API documents,
as described in the example previously.
We propose to address the issue by augmenting the type definitions based temporal constraints
with the constraints inferred from the natural language text in API documents.
Furthermore, such constraints although valuable but are already checked by any advanced 
Integrated Development Environment(IDE) such as eclipse for a strongly typed language.

>>>>

The increasing reach of internet has fueled the growth of web Application Programming Interfaces (API).
The ProgrammableWeb reports that the web APIs have doubled from Jan 2012 to Oct 2013\footnote{\url{http://www.programmableweb.com/api-research}}.
These APIs are being combined in interesting ways by application developers creating third-party applications using
these APIs to provide value added service.
For instance, many online stores leverage Paypal API to assist users with paying for the purchased commodities without actually
providing financial information to the online store.

Unlike most traditional API libraries that are in the format of locally stored binary files and are programming language specific,
web API are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, Web APIs like traditional APIs have rules or constraints governing the proper  use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints can result in faulty applications that are unreliable to use and may even result in financial losses.

In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
Thus compliance of such constraints are easily enforced by compilers.
In contrast to traditional API libraries, web APIs work on basic parameter data types such as \CodeIn{strings} and \CodeIn{numbers}.
Therefore enforcing temporal constraints through type system is ineffective in web APIs.
Additionally temporal constraints are not entirely restricted to type definitions.

Formal analysis tools such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in web API clients as defects~\cite{lee2012towards}.
However, such tools typically accept formal representation of the temporal constraints for detecting violations.
In contrast, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
in \amazonAPI\ documentation describe temporal constraints.

@@

Second, after API documents are made amenable to existing NLP techniques, a method referenced in the natural language text must be identified in order to infer temporal constraints on the method but such method referencing is often implicit.
Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method-invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively resource intensive and error-prone.
To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

@@

\begin{itemize}
	\item An NLP-based approach that effectively infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on \amazonAPI, \paypalAPI, and commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}

@@

%First, relying just on type information will result in an incomplete list of temporal constraints. 
%In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
%Voilations are easily detected by the IDE's
%For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
%that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
%However, using type system to detect temporal constraints in context of web APIs will result
%in a lot of false positives as web APIs work only on basic types such as
%\CodeIn{strings} and \CodeIn{numbers}.
%Use of basic datatype by web-apis result in search space explosion.
%Furthermore, we observed that temporal constraints re not limited to the type definitions
% 
%Our proposed approach extends the existing approaches to address the challenge.
%
%However, temporal constraints are not limited by the type definitions
%(i.e, requirements on the type of input parameters),
%and are currently expressed mostly in natural language in API documents,
%as described in the example previously.
%We propose to address the issue by augmenting the type definitions based temporal constraints
%with the constraints inferred from the natural language text in API documents.
%Furthermore, such constraints although valuable but are already checked by any advanced 
%Integrated Development Environment(IDE) such as eclipse for a strongly typed language.

### 2014-10-29 Draft/related.tex
Updated Introduction for flow Updated abstract with goal statement. Minor changes elsewhere.

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.

>>>>

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to relative well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
